A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and SVDCase cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability field. Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.

With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase. Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work). Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation.

>>>>

This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and SVDCase cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution. Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.

With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase. Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work). Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation \red{(SENTENCE IS SLIGHTLY CONFUSING ... NOT SURE WHAT YOU WANT TO CONVEY)}.
